Maps

### 2020-04-25 ms_8.Rmd
Commit all shiny components

library(shiny)
library(haven)
library(tidyverse)
library(gt)
library(devtools)
library(tibble)
library(foreign)
library(scales)
library(shinythemes)
library(plotly)
library(leaflet)
library(broom)
library(readxl)

@@

data1880j <- full_join(data1880a, data1880b, by = c("STATEA", "COUNTYA")) %>%
  mutate(GISJOIN = GISJOIN.x, YEAR = YEAR.x, STATE = STATE.x, COUNTY = COUNTY.x) %>%
  mutate(value_farm = APN001+APO001+APQ001, n_farm = AOQ001, cows =  AOG004+AOG005, horses = AOG001, 
         avg_size = APG001, value_implements = APO001, pop = AOT001, male = AP1001, female = AP1002, 
         enrolled = NA, urban_pop = AO4001, pct_urban = AO4001/AOT001*100, illiterate = NA, 
         acres_farms = AOR001, acres_irrigated = NA, pct_irrigated = NA) %>%
  mutate(cows_per_person = cows/n_farm, pct_enrolled = enrolled/pop*100, pct_illiterate = illiterate/pop*100) %>%
  select(STATEA, COUNTYA, GISJOIN, YEAR, STATE, COUNTY, value_farm, value_implements, avg_size, n_farm, 
         acres_farms, acres_irrigated, pct_irrigated, cows, cows_per_person, horses, pop, male, female, 
         enrolled, pct_enrolled, urban_pop, pct_urban, illiterate, pct_illiterate)

@@

data1890j <- full_join(data1890a, data1890b, by = c("STATEA", "COUNTYA")) %>%
  mutate(GISJOIN = GISJOIN.x, YEAR = YEAR.x, STATE = STATE.x, COUNTY = COUNTY.x) %>%
  mutate(value_farm = AUK001+AUK002+AUK003, n_farm = AS9001, cows = ASY002, horses = ASY003, 
         avg_size = ATW001, value_implements = AUK002, pop = AUM001, male = AV0001+AV0003+AV0005+AV0007, 
         female = AV0002+AV0004+AV0006+AV0008, enrolled = AVK005+AVK006+AVK007+AVK008, urban_pop = AUU001, 
         pct_urban = AUU001/AUM001*100, illiterate = NA, acres_farms = AUJ001+AUJ002, 
         acres_irrigated = AT2001, pct_irrigated = AT2001/(AUJ001+AUJ002)*100) %>%
  mutate(cows_per_person = cows/n_farm, pct_enrolled = enrolled/pop*100, pct_illiterate = illiterate/pop*100) %>%
  select(STATEA, COUNTYA, GISJOIN, YEAR, STATE, COUNTY, value_farm, value_implements, avg_size, n_farm, 
         acres_farms, acres_irrigated, pct_irrigated, cows, cows_per_person, horses, pop, male, female, 
         enrolled, pct_enrolled, urban_pop, pct_urban, illiterate, pct_illiterate)

@@

data1900j <- full_join(data1900a, data1900b, by = c("STATEA", "COUNTYA")) %>%
  mutate(GISJOIN = GISJOIN.x, YEAR = YEAR.x, STATE = STATE.x, COUNTY = COUNTY.x) %>%
  mutate(value_farm = AWV001, n_farm = AW3001, cows = AW7001, horses = AW7002, 
         avg_size = AXE001, value_implements = AWW003, pop = AWS001, male = AZ0001,female = AZ0001, 
         enrolled = NA, urban_pop = NA, pct_urban = NA, illiterate = AYS001+AYS002+AYS003+AYS004+AYS005, 
         acres_farms = AWT001, acres_irrigated = AX8001, pct_irrigated = AX8001/AWT001*100) %>%
  mutate(cows_per_person = cows/n_farm, pct_enrolled = enrolled/pop*100, pct_illiterate = illiterate/pop*100) %>%
  select(STATEA, COUNTYA, GISJOIN, YEAR, STATE, COUNTY, value_farm, value_implements, avg_size, n_farm, 
         acres_farms, acres_irrigated, pct_irrigated, cows, cows_per_person, horses, pop, male, female, 
         enrolled, pct_enrolled, urban_pop, pct_urban, illiterate, pct_illiterate)

@@

data1930j <- data1930j %>%
  mutate(GISJOIN = GISJOIN.x, YEAR = YEAR.x, STATE = STATE.x, COUNTY = COUNTY.x) %>%
  mutate(value_farm = BFD001+BFD002+BFD004+ACEO001, n_farm = AB95001, cows = NA, horses = NA, 
         avg_size = ACAA001, value_implements = BFD004, pop = BCX001, male = BC3001, 
         female = BC3002, enrolled = BDT001+BDT002+BDT003+BDT004, urban_pop = BDX001, 
         pct_urban = BDX001/BDP001*100, illiterate = BDV001, acres_farms = AB98001, 
         acres_irrigated = ACEX002, pct_irrigated = ACEX002/AB98001*100) %>%
  mutate(cows_per_person = cows/n_farm, pct_enrolled = enrolled/pop*100, pct_illiterate = illiterate/pop*100) %>%
  select(STATEA, COUNTYA, GISJOIN, YEAR, STATE, COUNTY, value_farm, value_implements, avg_size, n_farm, 
         acres_farms, acres_irrigated, pct_irrigated, cows, cows_per_person, horses, pop, male, female, 
         enrolled, pct_enrolled, urban_pop, pct_urban, illiterate, pct_illiterate)

@@

  mutate(value_farm = BWD001+BWD002, n_farm = BY1001, cows = NA, horses = NA, 
         avg_size = BY0001, value_implements = BWD002, pop = BVU001, male = BVY001, 
         female = BVY002, enrolled = BWU001+BWU002+BWU003+BWU004+BWU005, urban_pop = NA, 
         pct_urban = NA, illiterate = NA, acres_farms = BY3001, 
         acres_irrigated = NA, pct_irrigated = NA) %>%
  mutate(cows_per_person = cows/n_farm, pct_enrolled = enrolled/pop*100, 
         pct_illiterate = illiterate/pop*100) %>%
  select(STATEA, COUNTYA, GISJOIN, YEAR, STATE, COUNTY, value_farm, value_implements, avg_size, n_farm, 
         acres_farms, acres_irrigated, pct_irrigated, cows, cows_per_person, horses, pop, male, female, 
         enrolled, pct_enrolled, urban_pop, pct_urban, illiterate, pct_illiterate)

@@

  mutate(value_farm = B3M001, n_farm = B3Z001, cows = NA, horses = NA, 
         avg_size = B3L001, value_implements = NA, pop = B13001, male = B3E001, 
         female = B3E002, enrolled = B2A001+B2A002+B2A003+B2A004+B2A005, urban_pop = B2J001, 
         pct_urban = B2J001/B18001*101, illiterate = NA, acres_farms = B3K001, 
         acres_irrigated = NA, pct_irrigated = NA) %>%
  mutate(cows_per_person = cows/n_farm, pct_enrolled = enrolled/pop*100, pct_illiterate = illiterate/pop*100) %>%
  select(STATEA, COUNTYA, GISJOIN, YEAR, STATE, COUNTY, value_farm, value_implements, avg_size, n_farm, 
         acres_farms, acres_irrigated, pct_irrigated, cows, cows_per_person, horses, pop, male, female, 
         enrolled, pct_enrolled, urban_pop, pct_urban, illiterate, pct_illiterate)

@@

```{r experimentalModels}
# USE subData FOR ALL MODELS
# EVERYTHING ELSE IS DUBIOUS

# Incorporate
# Value of implements functions as a stand in for mechanization
impedu_plot <- allData %>%
  mutate(YEAR = as.factor(YEAR)) %>%
  group_by(YEAR) %>%
  select(YEAR, avg_value_implements, pct_enrolled) %>%
  na.omit() %>%
  ggplot(aes(x = avg_value_implements, y = pct_enrolled, color = YEAR)) + 
  geom_point(alpha = 0.1) +
  geom_smooth(method = "lm", se = FALSE) +
  ylim(0, 45) + 
  labs(title = "Relationship Between Farm Value and Education, by County",
       subtitle = "Midwestern United States", 
       x = "Average Value of Implements", 
       y = "Percent Population Enrolled in School") +
  scale_x_log10(labels = comma) +
  theme_classic()

# Incorporate
# States are gaining more implements each year
imp_plot <- allData %>%
  mutate(YEAR = as.factor(YEAR)) %>%
  select(YEAR, STATE, value_implements) %>%
  na.omit() %>%
  group_by(YEAR, STATE) %>%
  summarize(mean_imp = mean(value_implements)) %>% 
  ungroup() %>%
  group_by(STATE) %>%
  ggplot(aes(x = YEAR, y = mean_imp, fill = STATE)) + 
  geom_col() +
  labs(title = "Implement Value by Year, by State",
       subtitle = "Dollar Values Adjusted for Inflation",
       x = "Year",
       y = "Average Value of All Implements",
       fill = "State") +
  theme_classic()

@@

# INCORPORATE
# Effect of gender on enrollment dwindles over time
maleedu_plot <- maleedu_model %>%
  ungroup() %>%
  select(YEAR, pct_male_coef, pct_male_upper, pct_male_lower) %>%
  mutate(YEAR = as.factor(YEAR)) %>%
  group_by(YEAR) %>%
  ggplot(aes(x = YEAR, y = pct_male_coef)) + 
  geom_errorbar(ymin = maleedu_model$pct_male_lower, ymax = maleedu_model$pct_male_upper) + 
  geom_point() +
  theme_classic() +
  ylim(-1.5, 0.5) + 
  labs(x = "Year",
       y = "Coefficient",
       title = "Percent Male Coefficients Over Time",
       subtitle = "Measuring the effect of being male on school enrollment")

# avg_value_implements and cows_per_farm have an effect on enrollment
# in general, for 1879 and 1890, more cows per farm = less enrollment
# aka bigger farms = less enrollment?
model2a <- modelData %>% 
  filter(YEAR == "1870") %>%
  lm(data = ., pct_enrolled ~ cows_per_farm) %>% 
  tidy(conf.int = TRUE) %>% 
  select(term, estimate, p.value, conf.low, conf.high) %>%
  gt() %>% 
  fmt_number(data = ., columns = c("estimate", "p.value", "conf.low", "conf.high"), 
             decimals = 2)

# there was an infinite value left in the cows_per_farm column for this year
# not sure why, but I got rid of it
model2a <- modelData %>% 
  filter(YEAR == "1890", !is.infinite(cows_per_farm)) %>%
  lm(data = ., pct_enrolled ~ cows_per_farm) %>% 
  tidy(conf.int = TRUE) %>% 
  select(term, estimate, p.value, conf.low, conf.high) %>%
  gt() %>% 
  fmt_number(data = ., columns = c("estimate", "p.value", "conf.low", "conf.high"), 
             decimals = 2)

model2c <- modelData %>% 
  filter(YEAR == "1910") %>%
  lm(data = ., pct_enrolled ~ cows_per_farm) %>% 
  tidy(conf.int = TRUE) %>% 
  select(term, estimate, p.value, conf.low, conf.high) %>%
  gt() %>% 
  fmt_number(data = ., columns = c("estimate", "p.value", "conf.low", "conf.high"), 
             decimals = 2)

model2
# cow plot
# incorporate
cowplot <- modelData %>% 
  filter(YEAR == "1870" | YEAR == "1890" | YEAR == "1910") %>%
  ggplot(aes(x = cows_per_farm, y = pct_enrolled, color = YEAR)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_log10(labels = comma) +
  labs(title = "Cows and Education",
       subtitle = "Relationship between the number of cows per farm\nand school enrollment, by county",
       x = "Average Cows per Farm",
       y = "Percent of Population Enrolled in School") +
  theme_classic()

modelData %>% 
  filter(YEAR == "1870" | YEAR == "1890" | YEAR == "1910") %>%
  ggplot(aes(x = cows_per_farm, y = pct_enrolled, color = YEAR)) +
  geom_point() +
  geom_smooth(se = FALSE)

# Enrollment/Illiteracy model (just for testing)

# This is saying that for every 1% increase in illiterate people, there is a 0.24% 
# decrease in school enrollment, which makes sense
model3 <- modelData %>%
  lm(data = ., pct_enrolled ~ pct_illiterate) %>%
  tidy(conf.int = TRUE) %>%
  select(term, estimate, p.value, conf.low, conf.high) %>%
  gt() %>%
  fmt_number(data = ., columns = c("estimate", "p.value", "conf.low", "conf.high"), 
             decimals = 2)

mod3plot <- modelData %>%
  filter(! is.na(pct_enrolled) & ! is.na(pct_illiterate)) %>%
  ggplot(aes(pct_enrolled, pct_illiterate)) + 
  geom_point() + 
  geom_smooth(se = FALSE)
```

```{r moreModels}

# can only use percentages until adjusting for inflation
# OR deal with each year independently

# Set the NA values to almost zero
# Not ideal, but necessary for running regressions
# setting to zero returns NaNs

reg_years <- allData %>% 
  # sample the data to run faster
  # change this later
  sample_n(size = 5000) %>%
  # Get rid of the infinite cows_per_farm values
  filter(! (is.na(pct_enrolled) & is.na(avg_size))) %>%
  group_by(YEAR) %>%
  arrange(desc(YEAR)) %>% 
  nest()

  # Call map inside of mutate to add new columns to the tibble
  # reg_results are the results of the regression we ran in question 2
  # coef is the coefficient of log_migrants for each continent
  # upper and lower are the upper and lower bounds of the confidence interval created by tidy()

  # options
  #STATEA, COUNTYA, GISJOIN, YEAR, STATE, COUNTY, value_farm, value_implements, avg_size, n_farm, 
         # acres_farms, acres_irrigated, pct_irrigated, cows, cows_per_farm, horses, pop, male, female, 
        # enrolled, pct_enrolled, urban_pop, pct_urban, illiterate, pct_illiterate
reg_years1 <- reg_years %>%
  mutate(mod = map(data, ~ lm(pct_enrolled ~ avg_size + avg_value_implements + n_farm + pct_irrigated + cows_per_farm + pct_urban, data = .)),
         reg_results = map(mod, ~ tidy(., conf.int = TRUE)),
         avg_size_coef = map_dbl(reg_results, ~ filter(., term == "avg_size") %>% 
                                   pull(estimate)),
         avg_size_upper = map_dbl(reg_results, ~ filter(., term == "avg_size") %>% 
                                    pull(conf.high)),
         avg_size_lower = map_dbl(reg_results, ~ filter(., term == "avg_size") %>% 
                                    pull(conf.low)),
         avg_value_implements_coef = map_dbl(reg_results, ~ filter(., term == "avg_value_implements") %>% 
                                               pull(estimate)),
         avg_value_implements_upper = map_dbl(reg_results, ~ filter(., term == "avg_value_implements") %>% 
                                                pull(conf.high)),
         avg_value_implements_lower = map_dbl(reg_results, ~ filter(., term == "avg_value_implements") %>% 
                                                pull(conf.low)),
         n_farm_coef = map_dbl(reg_results, ~ filter(., term == "n_farm") %>% pull(estimate)),
         n_farm_upper = map_dbl(reg_results, ~ filter(., term == "n_farm") %>% pull(conf.high)),
         n_farm_lower = map_dbl(reg_results, ~ filter(., term == "n_farm") %>% pull(conf.low)),
         pct_irrigated_coef = map_dbl(reg_results, ~ filter(., term == "pct_irrigated") %>% pull(estimate)),
         pct_irrigated_upper = map_dbl(reg_results, ~ filter(., term == "pct_irrigated") %>% pull(conf.high)),
         pct_irrigated_lower = map_dbl(reg_results, ~ filter(., term == "pct_irrigated") %>% pull(conf.low)),
         cows_per_farm_coef = map_dbl(reg_results, ~ filter(., term == "cows_per_farm") %>% pull(estimate)),
         cows_per_farm_upper = map_dbl(reg_results, ~ filter(., term == "cows_per_farm") %>% pull(conf.high)),
         cows_per_farm_lower = map_dbl(reg_results, ~ filter(., term == "cows_per_farm") %>% pull(conf.low)),
         pct_urban_coef = map_dbl(reg_results, ~ filter(., term == "pct_urban") %>% pull(estimate)),
         pct_urban_upper = map_dbl(reg_results, ~ filter(., term == "pct_urban") %>% pull(conf.high)),
         pct_urban_lower = map_dbl(reg_results, ~ filter(., term == "pct_urban") %>% pull(conf.low))
  )

# Now use the resulting tibble to create the gt table

q4_gt <- q4 %>%

  # The original year column was giving me problems because it's a grouping variable
  # Ungrouping solved the problem

  ungroup() %>%

  select(YEAR, coef, lower, upper) %>%

  tab_header(title = "Title",
             subtitle = "With 95% Confidence Interval") %>%
  cols_label(YEAR = "Year", coef = "Migrant Coefficient", 
             lower = "Lower Bound", upper = "Upper Bound") %>%

  # Round all values to two decimal places

  fmt_number(columns = vars(coef, lower, upper), decimals = 2)

@@

@@

# PASTE DATA and LIBRARIES here after

# Input

ui <- fluidPage(

    # flatly is a nice theme to make the tabs look put together

    # Application title

    navbarPage("Agriculture and Education in the U.S.", theme = shinytheme("flatly"),

               # remember that tab panel is for what shows up in the tab, and title panel is 
               # for what shows up at the top of the page within the tab

               tabPanel("Tab 1",

                        # Give the page a title
                        titlePanel("Relationship Between Farm Value and Education, by County"),

                        # Generate a row with a sidebar
                        sidebarLayout(

                            # Define the sidebar with one input
                            # insteaad of region, I want year ######
                            sidebarPanel(
                                selectInput("year", "Year:", 
                                            choices=c("1870" = "1870", "1890" = "1890", "1910" = "1910"), 
                                            multiple = TRUE)),
                            helpText("From Great Plains Population and Environment Survey Agricultural and Social & Demographic Data.")
                        ),

                        # Create a spot for the plot
                        mainPanel(
                            tabsetPanel(id = "tabsMain",
                                        tabPanel("Plot",

                                                 # this tells the UI what plot to put

                                                 plotOutput("agPlot")  
                                        )))),
               tabPanel("Models",

                        # Give the page a title
                        titlePanel("Relationship Between Farm Value and Education, by County"),
                        p("Make some models! (See notes)"),
                        gt_output("model1")
               ),
               tabPanel("Maps",

                # Give the page a title
                titlePanel("Title Relating to Maps"),
                p("Add a slider for different years/variables & figure out how to get two maps side by side"),
                p("Maps may take up to 30 seconds to load."),
               leafletOutput("map1"),
               p()),

               tabPanel("About",

>>>>

library(shiny)
library(haven)
library(tidyverse)
library(gt)
library(devtools)
library(tibble)
library(foreign)
library(scales)
library(shinythemes)
library(plotly)
library(leaflet)
library(broom)
library(readxl)
library(gganimate)

@@

data1880j <- full_join(data1880a, data1880b, by = c("STATEA", "COUNTYA")) %>%
  mutate(GISJOIN = GISJOIN.x, YEAR = YEAR.x, STATE = STATE.x, COUNTY = COUNTY.x) %>%
  mutate(value_farm = APN001+APO001+APQ001, n_farm = AOQ001, cows =  AOG004+AOG005, horses = AOG001, value_implements = APO001, pop = AOT001, male = AP1001, female = AP1002, 
         enrolled = NA, urban_pop = AO4001, pct_urban = AO4001/AOT001*100, illiterate = NA, 
         acres_farms = AOR001, acres_irrigated = NA, pct_irrigated = NA) %>%
  mutate(avg_size = acres_farms/n_farm, cows_per_person = cows/n_farm, pct_enrolled = enrolled/pop*100, pct_illiterate = illiterate/pop*100) %>%
  select(STATEA, COUNTYA, GISJOIN, YEAR, STATE, COUNTY, value_farm, value_implements, avg_size, n_farm, 
         acres_farms, acres_irrigated, pct_irrigated, cows, cows_per_person, horses, pop, male, female, 
         enrolled, pct_enrolled, urban_pop, pct_urban, illiterate, pct_illiterate)

@@

data1890j <- full_join(data1890a, data1890b, by = c("STATEA", "COUNTYA")) %>%
  mutate(GISJOIN = GISJOIN.x, YEAR = YEAR.x, STATE = STATE.x, COUNTY = COUNTY.x) %>%
  mutate(value_farm = AUK001+AUK002+AUK003, n_farm = AS9001, cows = ASY002, horses = ASY003, value_implements = AUK002, pop = AUM001, male = AV0001+AV0003+AV0005+AV0007, 
         female = AV0002+AV0004+AV0006+AV0008, enrolled = AVK005+AVK006+AVK007+AVK008, urban_pop = AUU001, 
         pct_urban = AUU001/AUM001*100, illiterate = NA, acres_farms = AUJ001+AUJ002, 
         acres_irrigated = AT2001, pct_irrigated = AT2001/(AUJ001+AUJ002)*100) %>%
  mutate(avg_size = acres_farms/n_farm, cows_per_person = cows/n_farm, pct_enrolled = enrolled/pop*100, pct_illiterate = illiterate/pop*100) %>%
  select(STATEA, COUNTYA, GISJOIN, YEAR, STATE, COUNTY, value_farm, value_implements, avg_size, n_farm, 
         acres_farms, acres_irrigated, pct_irrigated, cows, cows_per_person, horses, pop, male, female, 
         enrolled, pct_enrolled, urban_pop, pct_urban, illiterate, pct_illiterate)

@@

data1900j <- full_join(data1900a, data1900b, by = c("STATEA", "COUNTYA")) %>%
  mutate(GISJOIN = GISJOIN.x, YEAR = YEAR.x, STATE = STATE.x, COUNTY = COUNTY.x) %>%
  mutate(value_farm = AWV001, n_farm = AW3001, cows = AW7001, horses = AW7002, value_implements = AWW003, pop = AWS001, male = AZ0001,female = AZ0001, 
         enrolled = NA, urban_pop = NA, pct_urban = NA, illiterate = AYS001+AYS002+AYS003+AYS004+AYS005, 
         acres_farms = AWT001, acres_irrigated = AX8001, pct_irrigated = AX8001/AWT001*100) %>%
  mutate(avg_size = acres_farms/n_farm, cows_per_person = cows/n_farm, pct_enrolled = enrolled/pop*100, pct_illiterate = illiterate/pop*100) %>%
  select(STATEA, COUNTYA, GISJOIN, YEAR, STATE, COUNTY, value_farm, value_implements, avg_size, n_farm, 
         acres_farms, acres_irrigated, pct_irrigated, cows, cows_per_person, horses, pop, male, female, 
         enrolled, pct_enrolled, urban_pop, pct_urban, illiterate, pct_illiterate)

@@

data1930j <- data1930j %>%
  mutate(GISJOIN = GISJOIN.x, YEAR = YEAR.x, STATE = STATE.x, COUNTY = COUNTY.x) %>%
  mutate(value_farm = BFD001+BFD002+BFD004+ACEO001, n_farm = AB95001, cows = NA, horses = NA, value_implements = BFD004, pop = BCX001, male = BC3001, 
         female = BC3002, enrolled = BDT001+BDT002+BDT003+BDT004, urban_pop = BDX001, 
         pct_urban = BDX001/BDP001*100, illiterate = BDV001, acres_farms = AB98001, 
         acres_irrigated = ACEX002, pct_irrigated = ACEX002/AB98001*100) %>%
  mutate(avg_size = acres_farms/n_farm, cows_per_person = cows/n_farm, pct_enrolled = enrolled/pop*100, pct_illiterate = illiterate/pop*100) %>%
  select(STATEA, COUNTYA, GISJOIN, YEAR, STATE, COUNTY, value_farm, value_implements, avg_size, n_farm, 
         acres_farms, acres_irrigated, pct_irrigated, cows, cows_per_person, horses, pop, male, female, 
         enrolled, pct_enrolled, urban_pop, pct_urban, illiterate, pct_illiterate)

@@

  mutate(value_farm = BWD001+BWD002, n_farm = BY1001, cows = NA, horses = NA, value_implements = BWD002, pop = BVU001, male = BVY001, 
         female = BVY002, enrolled = BWU001+BWU002+BWU003+BWU004+BWU005, urban_pop = NA, 
         pct_urban = NA, illiterate = NA, acres_farms = BY3001, 
         acres_irrigated = NA, pct_irrigated = NA) %>%
  mutate(avg_size = acres_farms/n_farm, cows_per_person = cows/n_farm, pct_enrolled = enrolled/pop*100, 
         pct_illiterate = illiterate/pop*100) %>%
  select(STATEA, COUNTYA, GISJOIN, YEAR, STATE, COUNTY, value_farm, value_implements, avg_size, n_farm, 
         acres_farms, acres_irrigated, pct_irrigated, cows, cows_per_person, horses, pop, male, female, 
         enrolled, pct_enrolled, urban_pop, pct_urban, illiterate, pct_illiterate)

@@

  mutate(value_farm = B3M001, n_farm = B3Z001, cows = NA, horses = NA, value_implements = NA, pop = B13001, male = B3E001, 
         female = B3E002, enrolled = B2A001+B2A002+B2A003+B2A004+B2A005, urban_pop = B2J001, 
         pct_urban = B2J001/B18001*101, illiterate = NA, acres_farms = B3K001, 
         acres_irrigated = NA, pct_irrigated = NA) %>%
  mutate(avg_size = acres_farms/n_farm, cows_per_person = cows/n_farm, pct_enrolled = enrolled/pop*100, pct_illiterate = illiterate/pop*100) %>%
  select(STATEA, COUNTYA, GISJOIN, YEAR, STATE, COUNTY, value_farm, value_implements, avg_size, n_farm, 
         acres_farms, acres_irrigated, pct_irrigated, cows, cows_per_person, horses, pop, male, female, 
         enrolled, pct_enrolled, urban_pop, pct_urban, illiterate, pct_illiterate)

@@

```{r experimentalModels}

# INCORPORATE ALL OF THESE IN SHINY

# Incorporate
# Value of implements functions as a stand in for mechanization
impedu_plot <- allData %>%
  mutate(YEAR = as.factor(YEAR)) %>%
  group_by(YEAR) %>%
  select(YEAR, avg_value_implements, pct_enrolled) %>%
  na.omit() %>%
  ggplot(aes(x = avg_value_implements, y = pct_enrolled, color = YEAR)) + 
  geom_point(alpha = 0.1) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_fill_viridis_d(aesthetics = "color") +
  ylim(0, 45) + 
  labs(title = "Relationship Between Farm Implements and Education, by County",
       subtitle = "Midwestern United States", 
       x = "Average Value of Implements", 
       y = "Percent Population Enrolled in School") +
  scale_x_log10(labels = comma) +
  theme_classic()

ggsave("final/impedu_plot.png", plot = impedu_plot)

# See implement plot (plot2) saved as gif

@@

# couldn't get gtsave to save to the "final" subdirectory
# will need to copy to "final" manually??
gtsave(data = maleedu_gt, filename = "maleedu_gt.html")

# INCORPORATE
# Effect of gender on enrollment dwindles over time
maleedu_plot <- maleedu_model %>%
  ungroup() %>%
  select(YEAR, pct_male_coef, pct_male_upper, pct_male_lower) %>%
  mutate(YEAR = as.factor(YEAR)) %>%
  group_by(YEAR) %>%
  ggplot(aes(x = YEAR, y = pct_male_coef)) + 
  geom_errorbar(ymin = maleedu_model$pct_male_lower, ymax = maleedu_model$pct_male_upper, color = "#453781FF") + 
  geom_point(color = "#440154FF") +
  theme_classic() +
  ylim(-1.5, 0.5) + 
  labs(x = "Year",
       y = "Coefficient",
       title = "Percent Male Coefficients Over Time",
       subtitle = "Measuring the effect of being male on school enrollment")

ggsave("final/maleedu_plot.png", plot = maleedu_plot)

# INCORPORATE
# more cows = more enrollment
cowedu_model <- allData %>%
  select(YEAR, pct_enrolled, cows_per_farm, avg_value_implements) %>%
  na.omit() %>%
  lm(pct_enrolled ~ cows_per_farm*avg_value_implements, data = .) %>%
  tidy(conf.int = TRUE)

cowedu_gt <- cowedu_model %>%
  select(term, conf.low, estimate, conf.high) %>%
  gt() %>%
  tab_header(title = "Effect Cows and Implements on Enrollment",
             subtitle = "With 95% Confidence Interval") %>%
  cols_label(term = "Coefficient Name", conf.low = "Lower Bound", estimate = "Estimated Value", conf.high = "Upper Bound") %>%
  fmt_number(columns = vars(conf.low, estimate, conf.high), decimals = 4)

# copy to "final"
gtsave(data = cowedu_gt, filename = "cowedu_gt.html")

# cow plot
# incorporate
cowedu_plot <- allData %>%
  select(YEAR, pct_enrolled, cows_per_farm) %>%
  na.omit() %>%
  mutate(YEAR = as.factor(YEAR)) %>%
  group_by(YEAR) %>%
  ggplot(aes(x = cows_per_farm, y = pct_enrolled, color = YEAR)) +
  geom_point(alpha = 0.1) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_viridis_d() +
  ylim(0, 45) +
  scale_x_log10(labels = comma) +
  labs(title = "Cows and Education",
       subtitle = "Relationship between the number of cows per farm\nand school enrollment, by county",
       x = "Average Cows per Farm",
       y = "Percent of Population Enrolled in School") +
  theme_classic()

ggsave("final/cowedu_plot.png", plot = cowedu_plot)

@@

```{r farmTrends}
# this takes foever--cache it

# INCORPORATE 
# just the gif files, not the whole code
# takes too long

# Trends in Midwestern Farming over Time

plot1a <- allData %>%
  select(YEAR, STATE, acres_farms, n_farm) %>%
  na.omit() %>%
  group_by(STATE, YEAR) %>%
  summarize(mean_acres = mean(acres_farms), mean_farm = mean(n_farm)) %>%
  ggplot(aes(x = YEAR, y = mean_acres, fill = STATE)) +
  geom_col() + 
  scale_fill_viridis_d() +
  labs(x = "Year",
       y = "Mean Acreage (Cumulative)",
       title = "Average Farmland Acreage over Time",
       fill = "State") +
  theme_classic() + 
  transition_states(YEAR, wrap = FALSE) +
  shadow_mark()

anim_save("final/plot1a.gif", plot1a)

plot1b_prep <- allData %>%
  select(YEAR, STATE, n_farm) %>%
  na.omit() %>%
  group_by(STATE, YEAR)

plot1b <- aggregate(plot1b_prep$n_farm, by = list(plot1b_prep$STATE, 
                                                  plot1b_prep$YEAR), FUN=sum) %>%
    mutate(STATE = Group.1, YEAR = Group.2, n = x) %>%
  ggplot(aes(x = YEAR, y = n, color = STATE)) +
  geom_line() + 
  scale_fill_viridis_d(aesthetics = "color") +
  labs(x = "Year",
       y = "Number of Farms",
       title = "Number of Farms over Time, by State",
       subtitle = "The number of farms increases from 1870 to the early 1900s, but is in decline by 1930",
       color = "State") +
    theme_classic() + 
    # animate
    transition_reveal(YEAR)

anim_save("final/plot1b.gif", plot1b)

# States are gaining more implements each year
plot2 <- allData %>%
  mutate(YEAR = as.factor(YEAR)) %>%
  select(YEAR, STATE, value_implements) %>%
  na.omit() %>%
  group_by(YEAR, STATE) %>%
  summarize(mean_imp = mean(value_implements)) %>% 
  ungroup() %>%
  group_by(STATE) %>%
  ggplot(aes(x = YEAR, y = mean_imp, fill = STATE)) + 
  geom_col() +
  scale_fill_viridis_d() +
  labs(title = "Implement Value by Year, by State",
       subtitle = "Dollar Values Adjusted for Inflation",
       x = "Year",
       y = "Average Value of All Implements",
       fill = "State") +
  theme_classic() + 
  transition_states(YEAR, wrap = FALSE) +
  shadow_mark()

anim_save("final/plot2.gif", plot2)

# Incorporate
# population plot

plot3_prep <- allData %>%
  select(YEAR, STATE, pop) %>%
  na.omit() %>%
  group_by(STATE, YEAR)

plot3 <- aggregate(plot3_prep$pop, by = list(plot3_prep$STATE, 
                                                  plot3_prep$YEAR), FUN=sum) %>%
    mutate(STATE = Group.1, YEAR = Group.2, n = x) %>%
  ggplot(aes(x = YEAR, y = n, color = STATE)) +
  geom_line() + 
  scale_fill_viridis_d(aesthetics = "color") +
  labs(x = "Year",
       y = "Population",
       title = "Midwest Population over Time, by State",
       color = "State") +
    theme_classic() + 
    # animate
    transition_reveal(YEAR)

anim_save("final/plot3.gif", plot3)

# Urbanization plot
# Urban = 2,500+

plot4_prep <- allData %>%
  select(YEAR, pop, urban_pop) %>%
  na.omit() %>%
  mutate(pop = pop-urban_pop)

plot4_prepb <- aggregate(plot4_prep$pop, by = list(plot4_prep$YEAR), 
                   FUN=sum) %>%
  mutate(YEAR = Group.1, n_pop = x)

plot4_prepc <- aggregate(plot4_prep$urban_pop, by = list(plot4_prep$YEAR), 
                   FUN=sum) %>% 
  mutate(YEAR = Group.1, n_urban_pop = x)

plot4_prepd <- full_join(plot4_prepb, plot4_prepc, by = c("YEAR")) %>%
  select(YEAR, n_pop, n_urban_pop) %>%
  mutate(YEAR = as.factor(YEAR)) %>%
  # convert to long format
  melt(id="YEAR")

limits4 <- c("1", "2", "3", "4", "5", "6", "7")
labels4 <- c("1870", "1880", "1890", "1910", "1920", "1930", "1950")

plot4 <- as_tibble(plot4_prepd) %>%
  # as.numeric is changing years to numbers 1:7
  mutate(YEAR = as.numeric(YEAR), variable = as.character(variable), 
         value = value/1000) %>%
  ggplot(aes(YEAR, value, color = variable)) +
  geom_line() +
  scale_x_discrete(limits = limits4, labels = labels4) +
  scale_fill_viridis_d(aesthetics = "color", breaks=c("n_urban_pop", "n_pop"), labels = c("Urban", "Rural")) +
  labs(x = "Year",
       y = "Population (in thousands)",
       title = "Midwest Urbanization",
       subtitle = "Rural and urban populations over Time",
       color = "") +
  theme_classic() +
  geom_point(aes(group = seq_along(YEAR))) +
  transition_reveal(YEAR)

anim_save("final/plot4.gif", plot4)
```

@@

# Paste here after
